Elephant Seal Age JAE Intraspecific Variation

### 2023-11-27 paper/paperv2.qmd
adding labels to supplemental plot

count(sealdat, year) %>% 
     left_join(as_tibble(ranef(breeding_mod_bad)$year, 
                         rownames = "year") %>% 
                   mutate(year = as.numeric(year)) %>% 
                   rename(coef = `(Intercept)`),
               by = "year") %>%
     ggplot(aes(n, coef, color = year)) +
     geom_point() +
     scale_color_gradient(low = "blue", high = "red") +
     theme_few()

>>>>

count(sealdat, year) %>% 
     left_join(as_tibble(ranef(breeding_mod_bad)$year, 
                         rownames = "year") %>% 
                   mutate(year = as.numeric(year)) %>% 
                   rename(coef = `(Intercept)`),
               by = "year") %>%
     ggplot(aes(n, coef, color = year, label = year)) +
     geom_point() + 
  geom_label() + 
     scale_color_gradient(low = "blue", high = "red") + 
     theme_few()
